\pagestyle{plain}
\begin{center}


\section*{Acknowledgements}
\singlespacing
Thanks to Marissa Allen, my collaborator on this project, and co-author of Chapter 1: Introduction and Chapter 5, section III: Potential Applications. \newline \newline
Special thanks Tim Tregubov, for working with us to develop the initial prototype for Foldlings, and for being a costant source of advice and technical help. \newline \newline
Special thanks to Kevin Baron and the Thayer Machine Shop at Dartmouth for assistance with laser cutting. \newline \newline
Thanks also to our advisors: Jodie Mack, Lorie Loeb, and Emily Whiting.  Particularly to Emily, whose guidance and comments on the software and thesis have been transformative. \newline \newline
Thanks to our first user: Rukmini Goswami.  Her feedback (and patience with our buggy software) were invaluable to us. \newline \newline
And thanks to Kiko Lam and Luke Zirngibl for their feedback throughout the process. \newline \newline \newline
We use a number of open-source packages in Foldlings:

\begin{itemize}
  \item \textbf{ANPathIntersection}: https://github.com/unixpickle/PathIntersection
  \item \textbf{CGPoint+Vector}: https://github.com/koher/CGPoint-Vector
  \item \textbf{ExSwift}: https://github.com/pNre/ExSwift
  \item \textbf{PerformanceBezier}: https://github.com/adamwulf/PerformanceBezier
  \item \textbf{SVGh}: https://github.com/GenerallyHelpfulSoftware/SVGgh
  \item \textbf{UIBezierPath+Interpolation}: https://github.com/jnfisher/ios-curve-interpolation
  \item \textbf{UIImage+AnimatedGif}: https://github.com/mayoff/uiimage-from-animated-gif \ldots
\end{itemize}

%\begin{itemize}
  % \item ANPathIntersection: \hyperref{https://github.com/unixpickle/PathIntersection} \ldots
% \end{itemize}

\end{center}

\doublespacing
\cleardoublepage
