\chapter{Conclusions}

We plan to release Foldlings in the Apple app store in September. In
many ways, the primary test of our software will be the extent to which
real users are able to achieve their design goals. However, we can make
several conclusions about the success of our tool.
\textbf{\textgreater{}\textgreater{}TODO: reference final user study}.
Additionally, we have qualitative evidence that suggest that users can
create a wide range of complex cards, faster and with more precision
than using manual methods. That said, there is much work to be done on
this and related popup-card design problems.

\section{User Interface Future Work}\label{user-interface-future-work}

\subsection{Modifications to the Master
Card}\label{modifications-to-the-master-card}

Currently, our software only allows for one size and type of master card
feature. That is, a greeting-card sized piece of paper, with a single
driving fold in the center. Allowing modifications to the driving fold
might allow users to change paper size, rotate the card so that the
middle fold is vertical, or construct a diagonal fold for the master
card.

\subsection{Multiple Cards}\label{multiple-cards}

Currently, our software. In order to support combinations of
interlocking foldlings, we would need to create an interface that allow
for connecting popup-card elements in 3D. Although very complex, this
could ultimately allow for a more complex arrangement of features that
our software currently affords (\citet{hart2007modular}).

\subsection{Safe Area Guides}\label{safe-area-guides}

Often, users wish construct a fully-contained popup card. That is, a
card that can close fully, with no portions of internal fold features
visible when the card is closed. In order to achieve this design in a
symmetrical card, all features with a driving fold must be within the
middle third of the card. We could add ``safe area'' guides and warnings
to indicate this area to users that want add that additional constraint
to their design.

\section{Algorithms \& Implementation Future
Work}\label{algorithms-implementation-future-work}

\subsection{Feature Intersections}\label{feature-intersections}

Feature intersections are only partially implemented, and do not always
succeed. To fully-implement feature intersections, we would need to
refactor our FoldFeature class to add feature intersections a primary
component. This would replace the current method of intersecting
features with folds --- \emph{splitFoldByOcclusion} --- and would allow
for more generalizable intersections between features.

\subsection{Concurrency}\label{concurrency}

A key limitation of Foldlings is that all functions currently run on a
single thread. As a consequence, the user is sometimes blocked by
operations that could be performed in the background. For example, when
completing a feature, out app ignores touch input until the feature is
added to the sketch and planes are calculated. This can cause a slight
but noticeable delay between Restructuring our algorithms to perform
computationally-heavy operations in the background would reduce lag
between action, allowing users to design more quickly and fluidly.

\section{Potential Applications}\label{potential-applications}

\emph{This section is co-authored with Marissa Allen}

As a general-purpose design tool for cuts and folds, Foldlings has a
wide variety of potential applications. For example, Melina Blees et al
present a graphene transistor that is constructed through kirigami
methods \citet{blees2014graphene}. Simple, usable interfaces for
designing complex kirigami structures are needed to advance similar
research.

One exciting application of Foldlings is as a tool for developing
advanced spatial reasoning skills. \citet{taylor2013think3d}. Since our
code is open source, advanced students could even modify our software to
develop new fold features and interactions.
